---
title: "CAVIAR ANNOTATION"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
knitr::opts_chunk$set(echo = TRUE)
```

# Overview
The ultimate goal here is to generate an annotation from mQTLs in delahaye. The required components must be generated for each CpG site:
1. LD matrix for all tested SNPs
2. SNP Z-score file

These components will then be used to get a continuous value for all SNPs tested at each CpG. We'll then take the the best (Maximum?) Value for each SNP and use this to define a continuous annotation to be used in LD score regression with a QTL GWAS. The question being answered is whether or not GWAS SNPs are more enriched in sex-specific mQTLs vs general mQTLs in placenta.

## LD matrix for tested SNPs
1. Generate SNP sets for each CpG
2. Use plink to calculate LD for these sets
```{r}
all_mQTLs <- fread("matrix_eqtl_data/cis_mQTL_9_methy_PC_all.txt")
```
### SNP Sets and Z scores
```{r}
probe_pos <- fread("matrix_eqtl_data/probe_pos.txt")
kg_snps <- fread("/arc/project/st-dennisjk-1/shared/data/1000G_phase3_info/ALL.wgs.phase3_shapeit2_mvncall_integrated_v5b.20130502.sites.vcf.gz", skip = "#CHROM", drop = c("QUAL", "FILTER", "INFO"))
mQTL_in_1kg <- all_mQTLs[SNP %chin% kg_snps[`#CHROM` == "22"]$ID]
for (cpg in unique(mQTL_in_1kg$gene)[1:10]) {
  chr <- probe_pos[geneid == cpg]$chr
  fwrite(
    mQTL_in_1kg[gene == cpg, .(SNP, Z = `t-stat`)],
    sprintf("caviar_files/%s/%s.z", chr, cpg),
    sep = "\t",
    col.names = FALSE,
    quote = FALSE
  )
}
```

### Compute LD and run CAVIAR
```{bash}
PLINK="/arc/project/st-dennisjk-1/software/plink1.9/plink"
CAVIAR="/arc/project/st-dennisjk-1/software/caviar/CAVIAR-C++/CAVIAR"
for i in 22; do
  for f in caviar_files/chr${i}/*.z;do
    time $PLINK --bfile /arc/project/st-dennisjk-1/shared/data/1000G_phase3_by_chr/plink/chr${i}\
      --allow-no-sex\
      --extract ${f}\
      --r square\
      --out ${f%.*}

    time $CAVIAR -o ${f%.*}.out \
      -l ${f%.*}.ld \
      -z ${f} \
      -r 0.95 \
      -c 2
    rm ${f%.*}.ld
  done
done

```
### Caviar dbugging
Certain probes aren't yielding LD files, so it's either something with z score write-out or plink that's getting errors:

```{bash}
cg03988279.ld
```

## Merge data
There's a limit of 1 million files on Sockeye, so I need to make sure I merge and delete data as it's generated:
```{r}

```
